A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-06-30 paper.tex
Add key upload description and figure

\subsection{Enable computation tasks delegation to broker with privacy}
To participate data subscription, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the resources of low-level devices are precious which should be used to focus on its jobs. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest to brokers. Note that the broker need to sign the digest, which has been proven to be key uploaded by a broker recorded on the Product Contract. The key upload times is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the session key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds.

@@

@@

\subsection{MAM Performance Evaluation}
MAM is a secure and validatable data storage of the proposed architecture. And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections. The interactions between data providers and MAM can be frequent. Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.

>>>>

\subsection{Enable computation tasks delegation to broker with privacy}
To manage data products and to benefit from trading, data providers have to interact with MAM and Ethereum smart contract while doing its original tasks. However, the resources of low-level devices are precious which should be used to focus on its jobs. Therefore, the operations of MAM and smart contracts are better to be delegated to brokers.

The delegation should ensure the privacy of data providers, for instance, brokers are asked to attach messages to MAM without knowing the contents as well as record encryption keys to smart contracts. To record encryption key to smart contract, data provider compute the digest of sensitive contents with hash function, and send the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key, otherwise the process is aborted. Note that the broker need to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract. The key upload times is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a refund to withdraw their funds. Fig.~\ref{fig:key_upload} demonstrate the key upload to Product Contract via a broker.

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

@@

\subsection{TA - endpoint}
\label{section:ta_endpoint}

@@

\subsection{MAM Performance Evaluation}
\label{section:mam_performance}
MAM is a secure and validatable data storage of the proposed architecture. And publishing data to MAM is the primary key to resolve all the difficulties discussed in previous sections. The interactions between data providers and MAM can be frequent. Data providers can either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace.
